### 2022-02-24 ANA-TOPQ-2019-17-PAPER-metadata.tex
updating to V0.5

%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used by the different cover pages.
%-------------------------------------------------------------------------------
% Title
%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
\AtlasTitle{Search for flavour-changing neutral current interactions of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.1em}}

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.5}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
\vspace{0.1em}
A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
Standard Model (SM) Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
%The Higgs boson decays into a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
Large Hadron Collider that corresponds to an integrated luminosity of 139 fb$^{-1}$.
Two processes are considered:  single top quark FCNC production in association with a Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one of top quarks decays into $Wb$ and the other decays into $qH$ through the FCNC interactions.
%top quark with FCNC decay of $t\rightarrow qH$. 
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ 
with an additional lepton (e,$\mu$),
as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
%Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
%No significant excess of events above the background expectation is found,
A slight excess of data is observed above the expected SM background with a significance of 2.6$\sigma$,
and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9 \times 10^{-4}$ ($5.0^{+2.2}_{-1.4}\times 10^{-4}$) and $7.2\times 10^{-4}$ ($3.6^{+1.7}_{-1.0}\times 10^{-4}$), respectively. 
The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$ for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
%$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.%}
% Author - this does not work with revtex (add it after \begin{document})
\author{The ATLAS Collaboration}

>>>>

%-------------------------------------------------------------------------------
% This file contains the title, author and abstract.
% It also contains all relevant document numbers used by the different cover pages.
%-------------------------------------------------------------------------------
% Title
%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
\AtlasTitle{Search for flavour-changing neutral current interactions of the top quark and the Higgs
boson which decays into a pair of $\tau$-leptons in pp collisions at $\sqrt{s}=13~\tev$ with the ATLAS detector\vspace{-0.10em} }

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
\AtlasVersion{0.5}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
\vspace{0.10em}
A search for flavour-changing neutral current (FCNC) $tqH$ interactions involving a top quark, an up-type quark ($q=u, c$), and a
Standard Model (SM) Higgs boson decaying into a $\tau$-lepton pair ($H\rightarrow \tau^+\tau^-$) is presented.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
Large Hadron Collider that corresponds to an integrated luminosity of 139 fb$^{-1}$.
Two processes are considered:  single top quark FCNC production in association with a Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one of top quarks decays into $Wb$ and the other decays into $qH$ through the FCNC interactions.
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ 
with an additional lepton (e,$\mu$),
as well as multiple jets. Event kinematics are used to separate signal from the background through a multivariate discriminant.  
A slight excess of data is observed above the expected SM background with a significance of 2.3$\sigma$,
and 95\% CL upper limits on the $t\to qH$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to cH$ and $t\to uH$ branching ratios of $9.9 \times 10^{-4}$ ($5.0^{+2.2}_{-1.4}\times 10^{-4}$) and $7.2\times 10^{-4}$ ($3.6^{+1.7}_{-1.0}\times 10^{-4}$), respectively. 
The corresponding combined observed (expected) upper limits on the dimension-6 operator Wilson coefficients in
the effective $tqH$ couplings are $C_{c\phi} <1.38\, (0.97)$ and $C_{u\phi} <1.18\, (0.83)$ for the new physics scale $\Lambda$ at 1~TeV, respectively.} 
%$|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.%}
% Author - this does not work with revtex (add it after \begin{document})
\author{The ATLAS Collaboration}

### 2022-02-24 sections/background_estimation.tex
updating to V0.5

Most background processes are modelled using MC simulation.
After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
Small contributions arise from single-top-quark, $W/Z$+jets, multi-jet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
with prompt leptons, i.e.\ those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
and the Higgs boson is forced to decay into $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as tau candidates, 
generically referred to as \texttt{fake} leptons, are estimated using data-driven methods. 
The background prediction is further improved during the statistical analysis by performing a likelihood 
fit to data using several signal-depleted control regions as discussed in Section~\ref{sec:strategy_Htautau}.

@@

In the hadronic channels, the contribution of fakes is estimated partially from data by defining control regions (CR)
enriched in misidentified
tau candidates via loosened tau requirements with proper fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
These CRs do not overlap with the main signal regions, discussed in Section~\ref{sec:strategy_Htautau}.
The CR selection requirements are analogous to those used to define signal regions, except
that the subleading tau candidate is required to fail the medium tau identification, but it still passes a loose requirement.
The contribution of fakes with subleading tau candidate can be calculated by rescaling the templates of loose taus in the CR
with fake factors (FF).
The templates are produced by subtracting all MC background contributions with real sub-leading taus from data.
The FFs are computed as
the ratio of the Data-MC ($\mathrm{real~tau}$) yields in which the tau candidate is passed or failed the medium tau ID selection
in the $W$+jets control region.
%passing to failing the medium tau ID in the $W$+jets control region.
%We have compared
FFs obtained from the $W$+jets and from the same-sign $\thadhad$ control regions are compared and the differences are treated as a systematic uncertainty.

>>>>

Most background processes are modelled using MC simulation.
After the event preselection, the main background is $\ttbar$ production, often in association with jets, denoted by $\ttbar$+jets in the following.
Small contributions arise from single-top-quark, $W/Z$+jets, multi-jet and diboson ($WW,WZ,ZZ$) production, as well as from the associated 
production of a vector boson $V$ ($V=W,Z$) or a Higgs boson and a $\ttbar$ pair ($\ttbar V$ and $\ttbar H$). All backgrounds 
with prompt leptons, i.e.\ those originating from the decay of a $W$ boson, a $Z$ boson, or a $\tau$-lepton,
are estimated using samples of simulated events and initially normalised to their theoretical cross sections.
In the simulation, the top-quark and SM Higgs boson masses are set to $172.5~\gev$ and $125~\gev$, respectively,
and the Higgs boson is forced to decay into $H\to \tau\tau$ with branching ratio calculated using \textsc{Hdecay}~\cite{Djouadi:1997yw}.  
Backgrounds with non-prompt light leptons (electron or muon), with photons or jets misidentified as electrons, or with jets misidentified as tau candidates, 
generically referred to as \texttt{fake} leptons, are estimated using data-driven methods. 
The background prediction is further improved during the statistical analysis by performing a likelihood 
fit to data using several signal-depleted control regions as shown in Table~\ref{tab:srcr}.

@@

In the hadronic channels, the contribution of fakes is estimated partially from data by defining control regions (CR)
enriched in misidentified
tau candidates via loosened tau requirements with proper fake factors and partially from MC~\cite{ATLAS-CONF-2021-044}.
These CRs do not overlap with the main signal regions, discussed in Section~\ref{sec:strategy_Htautau}.
The CR selection requirements are analogous to those used to define signal regions, except
that the subleading tau candidate is required to fail the medium tau identification, but it still passes a loose requirement.
The contribution of fakes with subleading tau candidate can be calculated by rescaling the templates of loose taus in the CR
with fake factors (FF).
The templates are produced by subtracting all MC background contributions with real subleading taus from data.
The FFs are computed as
the ratio of the Data-MC ($\mathrm{real~tau}$) yields in which the tau candidate is passed or failed the medium tau ID selection
in the $W$+jets control region.
%passing to failing the medium tau ID in the $W$+jets control region.
%We have compared
FFs obtained from the $W$+jets and from the same-sign $\thadhad$ control regions are compared and the differences are treated as a systematic uncertainty.

### 2022-02-24 sections/bdt_Htautau.tex
updating to V0.5

%-------------------------------------------------------------------------------
\section{Analysis strategy}
\label{sec:strategy_Htautau}
%-------------------------------------------------------------------------------

The analysis strategy adopted in the $\Htautau$ search is similar to the one used in Ref.~\cite{fcnc36,Chen:2015nta} but extended to more search channels.

\subsection{Event categorisation and kinematic reconstruction}
\label{sec:htautau_reco_cat}

The $tt(qH)$ and $tH$ signal being probed are characterised by the presence of $\tau$-leptons from the decay of 
the Higgs boson, where the remaining top quark decays into $Wb$. There is an additional $q$-jet from the FCNC $t\to qH$ decay in the top pair production. 
%at least  four (three) jets in the decay (production) mode, only one of which originates from a $b$-quark.
If the $W$ boson or one of the $\tau$-leptons decays leptonically, an isolated electron or muon, together with significant $\met$ is also expected.
In a significant fraction of the events, the lowest $\pt$ jet from the hadronic $W$ boson decay fails the minimum $\pt$ requirement of $25~\gev$,
resulting in only three reconstructed jets where the production mode is dominant. 
%some signal events mixed with production mode having only three reconstructed jets.
In order to optimise the sensitivity of the search, the selected events are categorised into seven SRs based on the number of light leptons,
$\had$ candidates, and on the number of light flavored jets:
$t_{\ell}\hadhad$, $t_{\ell}\had$-1j, $t_{\ell}\had$-2j, $t_h\lephad$-2j, $t_h\lephad$-3j, $t_h\hadhad$-2j, and $t_h\hadhad$-3j, as shown in Table~\ref{tab:srcr}.

%   \begin{table}
%   \centering
%   \caption{Overview of the signal regions and the control regions used for fake tau scale factor derivation in leptonic channels.}
%   \label{tab:srcr}
%   \begin{tabular}[h]{c|c|c|c|c|c|c}
%   \hline \hline
%   \multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
%   \multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & any                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
%   &$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
%   &$t_{\ell}\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
%   &$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
%   &$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
%   &$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
%   &$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
%   \multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & any                           & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
%   &$t_{\ell}t_{\ell}2b\tauhad$      & 2     & any                           & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
%   &$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
%   &$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
%   &$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
%   &$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
%   \end{tabular}
%   \end{table}

\begin{table}
\centering
\caption{Overview of the signal regions (SR) and the $t\bar{t}$ control regions (CRtt) used for fake tau scale factor derivation in leptonic channels. Leptons are required to have either same-sign (SS) or opposite-sign (OS) charges in each region.}
\label{tab:srcr}
\begin{tabular}[h]{c|c|c|c|c|c|c}
\hline \hline
\multicolumn{2}{c|}{Regions} & $b$-jet & light flavor jets        & lepton & hadronic taus & charge\\ \hline
\multirow{7}{*}{SR}&$t_{\ell}\thadhad$     & 1     & $\ge0$                                & 1      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_{\ell}\tauhad$-1j  & 1     & 1                                   & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}\tauhad$-2j  & 1     & 2                                        & 1      & 1                     & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_h\tlhad$-2j   & 1     & 2                           & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\tlhad$-3j   & 1     & $\ge3$                      & 1      & 1             & $\tlhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-2j & 1     & 2                            & 0      & 2             & $\thadhad$ OS\\ \cline{2-7}
&$t_h\thadhad$-3j & 1     & $\ge3$                       & 0      & 2             & $\thadhad$ OS\\ \hline
\multirow{6}{*}{CRtt}&$t_{\ell}t_{\ell}1b\tauhad$ & 1     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
&$t_{\ell}t_{\ell}2b\tauhad$      & 2     & $\ge0$                            & 2      & 1                     & $t_{\ell}t_{\ell}$ OS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-2jSS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-2jOS & 2     & 2                             & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-3jSS & 2     & $\ge3$                        & 1      & 1             & $t_{\ell}\tauhad$ SS\\ \cline{2-7}
&$t_{\ell}t_h2b\tauhad$-3jOS & 2     & $\ge3$                & 1      & 1             & $t_{\ell}\tauhad$ OS\\ \hline
\end{tabular}
\end{table}

%This event categorisation is primarily motivated by the different quality of the event kinematic reconstruction, depending on the amount 
%of $\met$ in the event (larger in $\lephad$ events compared with $\hadhad$ events), and whether a jet from the hadronic top-quark decay %is missing or not (events with exactly three jets or at least four jets).
This event categorisation is primarily motivated by optimizing the sensitivity in each signal region that targets either leptonic or hadronic top-quark
decays as well as the Higgs decays into either $\lephad$ or $\hadhad$ final states.   
The event kinematic reconstruction is used in the $t_h\hadhad$ and $t_h\lephad$ channels to suppress the background by constraining the
di-tau mass and the missing transverse energy in the event~\cite{Chen:2015nta}. 
%based on the strategy used in Ref.~\cite{Chen:2015nta}, and is summarised below.

For the $t_ht(qH)$ events, the jet from $t\to qH$, denoted as the FCNC jet ($q$-jet), should be a hard narrow jet from the
decay chain $t\to qH\to q\tau\tau$, with taus reconstructed as $\lephad$ or $\hadhad$.
There should be at least four jets among which the one with the smaller angular distance to the visible decay of the di-tau,
is considered as the $q$-jet since the FCNC top decay products are likely boosted closer together than other jets. 
If there are more than two jets besides the $q$- and $b$-jet, the jets from $W$ boson decay are chosen from the combination
with the invariant mass closest to the $W$ boson mass. There is the chance that one of the jets fails the $\pt$ requirement and is not reconstructed.
This kind of events will fall into $t_hH$ final state.
%while the FCNC top resonance is
%still reconstructable that the missing jet is likely from the decay of $W$ boson.
%given the big chance that the jet which is missing is from $W$ decay.
There are three jets coming from top hadronic decay including the $b$-jet and a pair of opposite-sign taus from the Higgs boson decay, where
both $t_h$ and $H$ can be reconstructed.  
%. So a Higgs resonance formed by the taus and a top resonance formed by
%the jets are expected.

The four-momenta of the invisible decay products from the decay of the $\tau$-leptons 
are estimated using a kinematics fit. The fit is done by minimising a $\chi^2$ function based on the Gaussian constraints on the Higgs boson mass and the
measured $\met$ within their expected resolutions. The resolution on the Higgs boson mass is assumed to be $20~\gev$, while the resolution on the measured $\met$ is parameterised as a linear function of 
$\sqrt{\sum E_{\text{T}}}$, where $\sum E_{\text{T}}$ is the scalar sum of the $\pt$ of all physics objects contributing to the $\met$ reconstruction~\cite{Aaboud:2018tkc}.
After the $\chi^2$ minimisation, the Higgs boson $\pt$ as well as the 
$\pt$ of the parent top quarks are determined with better resolution in the signal events.

For the  $t_{\ell}t(qH)$ and $t_{\ell}H$ events where $W$ boson from $t\to W b$ decay decays leptonically,
%has a large momentum and the flying direction is unknown.
the kinematic fit is no longer feasible due to extra neutrino from $W\rightarrow \ell\nu$ decay. The kinematic variables are calculated using the visible
objects only. After the event reconstruction, a number of variables are used to discriminate the signal from the background using a multivariate analysis described
in Section~\ref{sec:tmva}.

%With the event topology reconstructed, a number of variables are defined for signal and background separation used in the multivariate analysis discussed below.

%In the  $t_{\ell}t(qH)$ and $t_{\ell}H$ signal, the additional $q$ jet in the decay mode can still be found, but since the $W$ boson decays leptonically, there is a neutrino with large momentum and the flying direction is unknown. The kinematics fit is no longer feasible in the $t_{\ell}\hadhad$ channel. The variables calculated from the visible objects are directly used in the multivariate analysis. However, the kinematics fit is still performed for the $t_{\ell}\had$ channels where the lepton and $\had$ are treated as di-tau candidate.

\subsection{Multivariate discriminant}
\label{sec:tmva}

@@

 ${\pt}_{\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\

@@

\item ${\pt}_{\tau2}$ is the transverse momentum of the sub-leading tau candidate.
\item ${\pt}_{\ell}$ is the transverse momentum of the leading light lepton.

@@

\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tautau\text{q}}$.
\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the W candidate.

@@

\item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$, \text{i}=1,2 are the momentum fraction carried by the visible decay products from the leading and subleading tau decays. It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 

@@

\item $\Delta R(i,j)$ is the angular distance between \text{i} and \text{j} objects. 

@@

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit'). The uncertainty band includes both the statistical and systematic uncertainties in the background prediction. Overflow bins are included respectively in the last bin. Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) 
channels. 
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratios of the data to the background prediction.}
\label{fig:taupt_prefit}
\end{figure}

>>>>

\section{Multivariate discriminant}
\label{sec:tmva}

@@

 ${\pt}^{\ell}$                                 & $12$      &  $15$               &  $12$             & $17$     &       &  &         \\

@@

\item ${\pt}_{\tau2}$ is the transverse momentum of the subleading tau candidate.
\item ${\pt}^{\ell}$ is the transverse momentum of the leading light lepton.

@@

\item \text{min}($m_{\tau\tau \text{j}}$) is the visible mass of the di-tau candidates (include leptonic tau) and the light-flavor jet, minimized by choosing different jet, reflects the invariant masss of the visible FCNC top decaying product, an alternative to variable $m_{\tau\tau\text{q}}$.
\item \text{min}($m_{\text{jj}}$) is the invariant mass of two light-flavor jets, minimized by choosing different jets, reflects the invariant mass of the $W$ candidate.

@@

\item $E_{\tau\text{i}}/E_{\tau\text{i},\text{fit}}$ (\text{i}=1,2) is the momentum fraction carried by the visible decay products from the leading and subleading tau decays. It is based on the best-fit 4-momentum of the neutrino(s) according to the event reconstruction algorithm in this section. For the $\tauhad$ decay mode, the visible decay products carry most of the tau energy since there is only a single neutrino in the final state.% which is evident in the excess around 1 in Figure \ref{fig:x12_fit}. 

@@

\item $\Delta R(a,b)$ is the angular distance between \text{a} and \text{b} objects in the event. 

@@

%Figure~\ref{fig:asimov_prefitbdt} show the postfits to the data of BDT observable in each SRs with all background processes constrained to the SM expectation.
%The level of discrimination between signal and background achieved by the BDTs is illustrated in Figure~\ref{fig:overtrain_hadhad}-~\ref{fig:overtrain_lhadhad}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{\FCNCFigures/tex/BDTinput}
\begin{figure}[H]
\centering
\begin{tabular}{@{}ccc@{}}
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l2tau1bnj_os/tau_pt_0.pdf} &
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b1j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}&
%\includegraphics[page=7,width=0.33\textwidth]{\FCNCFigures/tthML/showFake/faketau/postfit/NOMINAL_fancpaper/reg1l1tau1b2j_ss_vetobtagwp70_highmet/tau_pt_0.pdf}\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l2tau1bnj_os.pdf} &
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b1j_ss.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_ss.pdf}\\
(a1) & (a2) & (a3) \\
%(a1) \pT(\tauhad) in $t_{\ell}\thadhad$ & (a2) \pT(\tauhad) in  $t_{\ell}\tauhad$-1j& (a3) \pT(\tauhad) in $t_{\ell}\tauhad$-2j\\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b2j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg1l1tau1b3j_os.pdf}&
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b2jos_vetobtagwp70_highmet.pdf}\\
(b1) & (b2) & (b3) \\
%(b1) \pT(\tauhad) in $t_h\tlhad$-2j & (b2) \pT(\tauhad) in  $t_h\tlhad$-3j & (b3) \pT(\tauhad) in $t_h\thadhad$-2j \\
\includegraphics[page=1,width=0.33\textwidth]{figures/new_pt/reg2mtau1b3jos_vetobtagwp70_highmet.pdf}&\\
(c1) \\
%(c1) \pT(\tauhad) in $t_h\thadhad$-3j\\
\end{tabular}
\caption{The leading $\thad$ $p_T$  distributions are compared between the expected background and $tuH$ signals in: $t_{\ell}\thadhad$ (a1),  $t_{\ell}\tauhad$-1j (a2),  $t_{\ell}\tauhad$-2j (a3), $t_h\tlhad$-2j (b1), $t_h\tlhad$-3j (b2), $t_h\thadhad$-2j (b3), and $t_h\thadhad$-3j (c1) before the fit to data ('Pre-Fit'). The uncertainty band includes both the statistical and systematic uncertainties in the background prediction. Overflow bins are included respectively in the last bin. Others (Rare) includes single top, and $V$+jets and other small backgrounds in the leptonic (hadronic) 
channels. 
%( only subtau real refers to $t\bar{t}$ MC with leading tau faked by other object, subleading tau from real contribution. 
The lower panels show the ratios of the data to the background prediction.}
\label{fig:taupt_prefit}
\end{figure}

### 2022-02-24 sections/data_presel.tex
updating to V0.5

The signal final state including an electron or muon or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ final states with $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
\item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay. Exactly one lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-jet.
\item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the lepton is required, including at least 2 jets with exactly one $b$-jet.
\end{itemize}

>>>>

The signal final state including a light lepton (electron or muon) or $\lep$ are referred to as leptonic channel, otherwise hadronic channel.
The events in the leptonic channel are recorded by single-electron or single-muon trigger, required to have exactly one electron or muon that matches, with $\Delta R < 0.15$, the lepton reconstructed by the trigger. Further requirements are defined targeting different signal decay modes:  
\begin{itemize}
\item $t_h\lephad$: Targeting $t_hH$ and $t_ht(qH)$ final states with $H\to\lephad$ decay. Exactly one $\had$ with opposite-side charge to $\lep$ is required, including at least three jets with exactly one $b$-jet.
\item $t_{\ell}\hadhad$: Targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay. Exactly a light lepton and two opposite-sign $\had$ are selected, including at least 1 jet with exactly one $b$-jet.
\item $t_{\ell}\had$: Also targeting $t_{\ell}H$ and $t_{\ell}t(qH)$ final states with $H\to\hadhad$ decay when one of the $\had$ fails the tau reconstruction or identification so that there is only
  one $\had$ candidate reconstructed. Exactly one $\had$ with same-sign charge to the light lepton is required, including at least 2 jets with exactly one $b$-jet.
\end{itemize}
